\sysfull

### 2017-08-11 paper/evaluation.tex

\begin{table}[t]
	\centering
	\footnotesize
        \renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{|l|cc|cc|cc|cc|c|}
		\hline
		{} & \multicolumn{2}{c|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & & & $<$1\\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand).\todo{Data for dd, dft, sort missing}{Kiwan}}
\label{table:compiler_result}
\end{table}

We start with evaluating the efficiency of the \sys compiler Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging calls\todo{calls or code? what is paging call?}{Kiwan} in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%. The results indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, the \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer aliasing. Thus, it results in the \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provided in Section~\ref{sec:result_compiler_time}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise the compiler can be used to simplify the programmability.

>>>>

\begin{table}[t]
	\centering
	\footnotesize
        \renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{|l|cc|cc|cc|cc|c|}
		\hline
		{} & \multicolumn{2}{c|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & 180 & 287 & $<$1\\
		dft* & - & - & - & - & - & - & 222 & 293 & -\\
		dd &  &  &  &  &  &  &  & 287 &  \\
		\hline
	\end{tabular}
	\caption{Comparison between \sys and Chain source code line number (SLOC column) and comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Man.) (other columns). *DFT does not compile with Clang\todo{incomplete table}{Responsible:Kiwan}}
\label{table:compiler_result}
\end{table}

We start with evaluating the efficiency of the \sys compiler Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging macro ({\tt RVAR} and {\tt WVAR}) in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%. The results indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, the \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer aliasing. Thus, it results in the \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provided in Section~\ref{sec:result_compiler_time}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise the compiler can be used to simplify the programmability.
